Owlifier: Creating OWL-DL Ontologies from Simple Spreadsheet-Based Knowledge Descriptions\tnoteref{t1}

### 2008-12-01 docs/pubs/ISEI6/main.tex
up to relationship blocks

\newcommand{\Owlifier}{\textsf{Owlifier}}
\newcommand{\owlifier}{\textsf{owlifier}}
\newcommand{\mypara}[1]{\vspace{12pt}\noindent\textbf{#1}}

@@

An \owlifier\ table defines an OWL-DL
\cite{smith04:_owl_web_ontol_languag_guide} ontology through a set of
\emph{blocks} representing one or more ontology definitions.  Each
non-empty row in an \owlifier\ table corresponds to a block. The type
of the block is given in the first column of the row. We describe each
type of block supported by \owlifier\ below. Here we assume that if
any of the properties or concepts used in a block are defined, i.e.,
are not imported from another ontology, then they are added to the
ontology being defined by the \owlifier\ table.

\mypara{Import Block.} Import blocks assign namespace labels to
external ontologies. Each external ontology is imported into the
current ontology. We refer to the ontologies of import blocks as
\emph{imported ontologies}.  Using import blocks, classes and
properties of imported ontologies can be used within other blocks of
an \owlifier\ table.  Import blocks take the form
\begin{itemize}
\item[]
  \begin{tabular}{|l|l|l|}\hline
    \texttt{import} & $\textit{N}$ & $\textit{U}$ \\ \hline 
  \end{tabular} 
\end{itemize}
where $\textit{N}$ is a namespace label and $\textit{U}$ is an OWL
ontology URI. Classes and properties from imported ontologies are
referenced by prefixing the namespace label $\textit{N}$ to the
corresponding class or property name in the normal way. The following
block imports the ``earth realm'' ontology from the set of SWEET
ontologies \cite{raskin:_seman_web_for_earth_and}
\begin{tabbing}
  ~~\texttt{import sweet
    http://sweet.jpl.nasa.gov/ontology/earthrealm.owl}
\end{tabbing}
where the ontology class denoting marine ecosystems can be refered to
from within the corresponding \owlifier\ table using the syntax, e.g.,
\sloppy\texttt{sweet:MarineEcosystem}. Because this class refers to a
class in another ontology, we call it an ``imported'' class.

\mypara{Entity Block.} Entity blocks introduce new OWL classes and
specify subclass relationships. Imported classes may also be used
within a concept block by prefixing the class name with a namespace
label, e.g., when an ontology is being extended.  We use the term
`entity to avoid confusion with the use of the term 'class' in
biological taxonomies and because `entity' is used in \cite{oboe} to
define ecological concepts. Entity blocks take the form
\begin{itemize}
\item[] 
  \begin{tabular}{|l|l|l|l|l|}\hline
    \texttt{entity} & $C_1$ & $C_2$ & \dots & $C_n$ \\ \hline 
  \end{tabular} \hfill ($n \ge 1$)
\end{itemize}
where each class $C_i$ is asserted in the current ontology to subsume
a class $C_{i+1}$, for $1 \le i < n$. Each $C_i$ in a concept block
induces the DL axiom \[C_i \sqsubseteq C_{i+1}.\] If both $C_i$ and
$C_{i+1}$ are imported classes, we say that the block defines an
``articulation'' (i.e., mapping) between the two classes. The
following concept block defines a simple subclass hierarchy
\begin{tabbing}
  ~~\texttt{entity PhysicalFeature AquaticPhysicalFeature River}
\end{tabbing}
which states that river is a subclass of aquatic physical feature and
that aquatic physical feature is a subclass of physical feature.

\mypara{Synonym Block.} Synonym blocks define an equivalence
relationship between classes.  A synonym block has the form
\begin{itemize}
\item[] 
  \begin{tabular}{|l|l|l|l|l|}\hline
    \texttt{synonym} & $C_1$ & $C_2$ & \dots & $C_n$ \\ \hline 
  \end{tabular} \hfill ($n \ge 2$)
\end{itemize}
where each class $C_i$ is asserted as being equivalent to class
$C_{i+1}$ in the current ontology, for $1 \le i < n$. For example, the
block
\begin{tabbing}
~~\texttt{synonym Maize Corn}
\end{tabbing}
defines maize and corn as synonym (i.e., equivalent) classes.

\mypara{Overlap Block}

\mypara{}Except in certain situations (described further below),
classes are assumed to be disjoint.  Overlap blocks explicitly relax
this assumption for a given set of classes by stating that a set of
classes may have overlapping instances. An overlap block has the form
\begin{itemize}
\item[] 
  \begin{tabular}{|l|l|l|l|l|}\hline
    \texttt{overlap} & $C_1$ & $C_2$ & \dots & $C_n$ \\ \hline 
  \end{tabular} \hfill ($n \ge 2$)
\end{itemize}
where each class $C_i$ is allowed to share instances with each concept
$C_j$, for $1 \le i,j \le n$. In particular, $C_i$ and $C_j$ are not
defined to be disjoint classes in the current ontology.

--- an example here ---

\mypara{Relationship Block}

\mypara{}Relationship blocks define required \emph{object} properties
of classes. A property block has the form
\begin{itemize}
\item[]
  \begin{tabular}{|l|l|l|l|l|l|}\hline \texttt{relationship} & $R$ & $C_1$
    & $C_2$ & \dots & $C_n$ \\ \hline
  \end{tabular} \hfill ($n \ge 2$)
\end{itemize}
where $R$ is an object property and each $C_i$ is a class, for $1 \le
i \le n$.  For every class $C_i$, the property block induces the DL
axiom \[C_i \sqsubseteq \exists R . C_{i+1} \] stating that each
instance of $C_i$ has, amongst possibly other things, a relationship
through $R$ to some instance of $C_{i+1}$.  The following example
\begin{tabbing}
   ~~need example here
\end{tabbing}

\mypara{Transitive Block}

\mypara{}Transitive blocks state that a property is transitive. That
is, if $P$ is transitive and a concept instance $O_1$ is related to an
instance $O_2$ by $P$, and $O_2$ is related to an instance $O_3$ by
$P$, then $O_1$ is also by definition related to $O_3$ by $P$. A
transitive block has the form
\begin{itemize}
\item[]
  \begin{tabular}{|l|l|l|l|l|l|}\hline \texttt{transitive} & $R$ & $C_1$
    & $C_2$ & \dots & $C_n$ \\ \hline
  \end{tabular} \hfill ($n \ge 2$)
\end{itemize}
where $P$ is an object property. For example, the block
\begin{quote}\texttt{transitive} \texttt{hasPart} \texttt{Body}
  \texttt{Head} \texttt{Eye} \texttt{Retina}
\end{quote} states that a body has at least one head, a head has at
least one eye, and an eye has at least one retina.

\paragraph{Attribute Block.} Attribute blocks are used to define the
required \emph{datatype} properties of concepts. An attribute block
has the form
\begin{itemize}
\item[]
  \begin{tabular}{|l|l|l|l|l|l|l|}\hline \texttt{attribute} & $P$ & $D$ & $C_1$
    & $C_2$ & \dots & $C_n$ \\ \hline
  \end{tabular} \hfill ($n \ge 1$)
\end{itemize}
where $P$ is a datatype property, each $C_i$ is a concept for $1 \le i
\le n$, and $D$ is a datatype (\texttt{anyValueType}, \texttt{string},
\texttt{int}, etc.). For every concept $C_i$, the property block
induces the DL axiom \[C_i \sqsubseteq (\exists P . D)\] stating that
each instance of $C_i$ has, amongst possibly other things, a
relationship through $P$ to a data value of type $D$.

\paragraph{Value Block.} Value blocks define required datatype
property \emph{constant values} for concepts. A value block has the
form
\begin{itemize}
\item[]
  \begin{tabular}{|l|l|l|l|l|l|l|}\hline \texttt{value} & $P$ & $V$ & $C_1$
    & $C_2$ & \dots & $C_n$ \\ \hline
  \end{tabular} \hfill ($n \ge 1$)
\end{itemize}
where $P$ is a datatype property, $C_i$ is a concept for $1 \le i \le
n$, and $V$ is a datatype value. For each concept $C_i$, the value
block induces the DL axiom \[C_i \sqsubseteq (V \in P)\] stating that
each instance of $C_i$ has a value $V$ for property $P$.  The value
restrictions stated by value blocks are often used for defining
so-called \emph{value partitions} \cite{co-ode}.

\paragraph{Inverse Block.} Inverse blocks state that two object
properties are inverses of each other. That is, for inverse properties
$P_1$ and $P_2$ and concept instances $O_1$ and $O_2$, if $P_1(O_1) =
O_2$, then $P_2(O_2) = O_1$.  An inverse block has the form
\begin{itemize}
\item[]
  \begin{tabular}{|l|l|l|}\hline \texttt{inverse} & $P_1$ & $P_2$
\\ \hline
  \end{tabular}
\end{itemize}
where $P_1$ and $P_2$ are object properties.

\paragraph{Minimum Block.} Minimum blocks state the minimum
number of properties $P$ an instance of a concept may have.
Minimum blocks have the form
\begin{itemize}
\item[]
  \begin{tabular}{|l|l|l|l|l|l|l|}\hline \texttt{minimum} & $P$ & $N$ & 
    $C_1$ & $C_2$ & $\dots$ & $C_m$
    \\ \hline
  \end{tabular}
\end{itemize}
where $N$ is the minimum number of properties $P$ that instances of
concept $C_1$ may have to instances of concept $C_2$, $C_2$ to $C_3$,
and so on. A cardinality block induces the DL axiom \[C_i \sqsubseteq
(\le N P.C_{i+1})\] stating that each instance of $C_i$ must be related to
at least $N$ unique instances of $C_{i+1}$ via $P$. For example, the blocks
\begin{quote}
\texttt{minimum} \texttt{hasPart} 1 \texttt{Body} \texttt{Head} \\
\texttt{minimum} \texttt{hasPart} 2 \texttt{Head} \texttt{Eye}
\end{quote}
states that a body has at least one head and at least two eyes.

\paragraph{Maximum Block.} Maximum blocks state the maximum
number of properties $P$ an instance of a concept may have.
Maximum blocks have the form
\begin{itemize}
\item[]
  \begin{tabular}{|l|l|l|l|l|l|l|}\hline \texttt{maximum} & $P$ & $N$ & 
    $C_1$ & $C_2$ & $\dots$ & $C_m$
    \\ \hline
  \end{tabular}
\end{itemize}
where $N$ is the maximum number of properties $P$ that instances of
concept $C_1$ may have to instances of concept $C_2$, $C_2$ to $C_3$,
and so on. A cardinality block induces the DL axiom \[C_i \sqsubseteq
(\ge N P.C_{i+1})\] stating that each instance of $C_i$ may be related to
at most $N$ unique instances of $C_{i+1}$ via $P$. For example, the blocks
\begin{quote}
\texttt{maximum} \texttt{hasPart} 1 \texttt{Body} \texttt{Head} \\
\texttt{maximum} \texttt{hasPart} 2 \texttt{Head} \texttt{Eye}
\end{quote}
states that a body has at least one head and at least two eyes.

\paragraph{Sufficient Block.} Sufficient blocks state that any
instance having a property $P$ to an instance of a concept $C_2$ is a
sufficient condition for being an instance of a concept $C_1$. A
sufficient block has the form
\begin{itemize}
\item[]
  \begin{tabular}{|l|l|l|l|}\hline \texttt{sufficient} & $C_1$ & $P$ & $C_2$
    \\ \hline
  \end{tabular}
\end{itemize}
where $C_1$ is the target concept (i.e., denoting the concept
definition), $P$ is the sufficient property, and $C_2$ is the
sufficient concept. A sufficient block induces the DL axiom \[C_1
\equiv \exists P.C_2\] Sufficient blocks provide a mechansism to
construct simple class definitions (i.e., classes defined precisely by
other classes), primarily for use with value partitions. [NOTE: these
should be anded together?]

\paragraph{Description Block.} Description blocks assign plain-text
definitions to concepts and properties. A description block has the
form
\begin{itemize}
\item[]
  \begin{tabular}{|l|l|l|}\hline \texttt{description} & $T$ & $S$
\\ \hline
  \end{tabular}
\end{itemize}
where $T$ is either a property or a concept and $S$ is a description
string.

\paragraph{Note Block.} Note blocks add comments to the current
ontology, and are ignored by \owlifier.  A note block has the form
\begin{itemize}
\item[]
  \begin{tabular}{|l|l|l|}\hline \texttt{note} & $S$
\\ \hline
  \end{tabular}
\end{itemize}
where $S$ is a comment string.

>>>>

\newcommand{\Owlifier}{\textsf{Owlifier}}
\newcommand{\owlifier}{\textsf{owlifier}}

\newcommand{\myblock}[1]{\vspace{12pt}\noindent\textbf{#1}}

@@

An \owlifier\ table defines an OWL-DL
\cite{smith04:_owl_web_ontol_languag_guide} ontology through a set of
\emph{blocks} representing one or more ontology definitions.  Each
non-empty row in an \owlifier\ table corresponds to a block. The type
of the block is given in the first column of the row. We describe each
type of block supported by \owlifier\ below. Here we assume that if
any properties or classes used in a block are undefined, i.e., are not
imported from another ontology, then they are added to the ontology
being specified via the \owlifier\ table. In general, we name blocks
according to the more generic terms used in
\cite{bowers08:_concep_model_framew_for_expres,madina07:_ontol_for_descr_and_synth}
instead of those of OWL-DL. This allows \owlifier\ to generate
ontologies that extend the observational model of
\cite{madina07:_ontol_for_descr_and_synth} for data annotation, and in
certain cases avoids confusion with established terms used within
biology.

\myblock{Import Blocks.} Import blocks assign namespace labels to
external ontologies. Each external ontology is imported into the
current ontology. We refer to the ontologies of import blocks as
\emph{imported ontologies}.  Using import blocks, classes and
properties of imported ontologies can be used within other blocks of
an \owlifier\ table.  Rows containing import blocks take the form
\begin{itemize}
\item[]
  \begin{tabular}{|l|l|l|}\hline
    \texttt{import} & $n$ & $u$ \\ \hline 
  \end{tabular} 
\end{itemize}
where $n$ is a namespace label and $u$ is an OWL ontology URI. Classes
and properties from imported ontologies are referenced by prefixing
the namespace label $n$ to the corresponding class or property name in
the normal way. The following example block imports the ``earth
realm'' ontology from the set of SWEET ontologies
\cite{raskin:_seman_web_for_earth_and}
\begin{tabbing}
  ~~\texttt{import sweet
    http://sweet.jpl.nasa.gov/ontology/earthrealm.owl}
\end{tabbing}
With this import block the class denoting marine ecosystems can be
referred to from within an \owlifier\ table using the expression
\texttt{sweet:MarineEcosystem}. Because this class refers to a class
in another ontology, we refer to it as an \emph{imported class}.

\myblock{Entity Blocks.} Entity blocks introduce new OWL classes and
specify subclass relationships. Imported classes may also be used
within entity blocks by prefixing class names with namespace labels
(see above).  We use the term `entity' to conform to the observational
model of \cite{bowers08:_concep_model_framew_for_expres} and to avoid
confusion with the term 'class' used within biological
taxonomies. Rows containing entity blocks take the form
\begin{itemize}
\item[] 
  \begin{tabular}{|l|l|l|l|l|}\hline
    \texttt{entity} & $c_1$ & $c_2$ & \dots & $c_n$ \\ \hline 
  \end{tabular} \hfill ($n \ge 1$)
\end{itemize}
where each $c$ is a class, and each $c_i$ is asserted in the current
ontology to subsume $c_{i+1}$, for $1 \le i < n$. That is, each $c_i$
in a concept block induces the description-logic axiom $c_{i+1}
\sqsubseteq c_i$.  If both $c_i$ and $c_{i+1}$ are imported classes,
we say that the block defines an ``articulation'' (i.e., mapping)
between the two classes. The following concept block defines a simple
subclass hierarchy
\begin{tabbing}
  ~~\texttt{entity PhysicalFeature AquaticPhysicalFeature River}
\end{tabbing}
stating that Physical Feature, Aquatic Physical Feature, and River are
classes, and that River is a subclass of Aquatic Physical Feature, and
Aquatic Physical Feature is a subclass of Physical Feature.

\myblock{Synonym Blocks.} Synonym blocks define equivalence
relationships between ontology classes.  Rows containing synonym
blocks take the form
\begin{itemize}
\item[] 
  \begin{tabular}{|l|l|l|l|l|}\hline
    \texttt{synonym} & $c_1$ & $c_2$ & \dots & $c_n$ \\ \hline 
  \end{tabular} \hfill ($n \ge 2$)
\end{itemize}
stating that each class $c_i$ is equivalent to class $c_{i+1}$ in the
current ontology, for $1 \le i < n$. Each $c_i$ in a synonym blocks
induces a description logic axiom of the form $c_i \equiv c_{i+1}$. As
an example, the block
\begin{tabbing}
~~\texttt{synonym Maize Corn}
\end{tabbing}
defines Maize and Corn as synonym (i.e., equivalent) classes.

\myblock{Overlap Blocks.} Except in certain situations (see
\secref{sec:properties}), classes are assumed to be disjoint.  Overlap
blocks explicitly relax this assumption by stating that a set of
classes may have overlapping instances. Rows containing overlap blocks
take the form
\begin{itemize}
\item[] 
  \begin{tabular}{|l|l|l|l|l|}\hline
    \texttt{overlap} & $c_1$ & $c_2$ & \dots & $c_n$ \\ \hline 
  \end{tabular} \hfill ($n \ge 2$)
\end{itemize}
stating that each class $c_i$ is allowed to share instances with each
class $c_j$, for $1 \le i,j \le n$. In particular, a given $c_i$ and
$c_j$ in an overlap block are not defined to be disjoint classes in
the current ontology. As an example, consider the following entity
blocks that define the classes Estuary, Lagoon, and Marsh as
subclasses of Ecological Habitats.
\begin{tabbing}
\begin{tabular}{lll}
  \texttt{entity} & \texttt{EcologicalHabitat} & \texttt{Estuary} \\ 
  \texttt{entity} & \texttt{EcologicalHabitat} & \texttt{Lagoon} \\ 
  \texttt{entity} & \texttt{EcologicalHabitat} & \texttt{Marsh} \\ 
\end{tabular}
\end{tabbing}
Given only these blocks, \owlifier\ treats Estuary, Lagoon, and Marsh
as disjoint classes. To relax this assumption and allow Lagoons to
also be kinds of Estuaries, we explicitly define the overlap block
\begin{tabbing}
\begin{tabular}{lll}
  \texttt{overlap} & \texttt{Estuary} & \texttt{Lagoon}
\end{tabular}
\end{tabbing}
In general, overlap blocks are rarely used but provide a mechanism to
override the default behavior of \owlifier\ in asserting disjoint
classes.

\myblock{Relationship Blocks.} Relationship blocks define required
\emph{object} properties of classes. A property block has the form
\begin{itemize}
\item[]
  \begin{tabular}{|l|l|l|l|l|l|}\hline \texttt{relationship} & $R$ & $C_1$
    & $C_2$ & \dots & $C_n$ \\ \hline
  \end{tabular} \hfill ($n \ge 2$)
\end{itemize}
where $R$ is an object property and each $C_i$ is a class, for $1 \le
i \le n$.  For every class $C_i$, the property block induces the DL
axiom \[C_i \sqsubseteq \exists R . C_{i+1} \] stating that each
instance of $C_i$ has, amongst possibly other things, a relationship
through $R$ to some instance of $C_{i+1}$.  The following example
\begin{tabbing}
   ~~need example here
\end{tabbing}

\myblock{Transitive Blocks.} Transitive blocks state that a property
is transitive. That is, if $P$ is transitive and a concept instance
$O_1$ is related to an instance $O_2$ by $P$, and $O_2$ is related to
an instance $O_3$ by $P$, then $O_1$ is also by definition related to
$O_3$ by $P$. A transitive block has the form
\begin{itemize}
\item[]
  \begin{tabular}{|l|l|l|l|l|l|}\hline \texttt{transitive} & $R$ & $C_1$
    & $C_2$ & \dots & $C_n$ \\ \hline
  \end{tabular} \hfill ($n \ge 2$)
\end{itemize}
where $P$ is an object property. For example, the block
\begin{quote}\texttt{transitive} \texttt{hasPart} \texttt{Body}
  \texttt{Head} \texttt{Eye} \texttt{Retina}
\end{quote} states that a body has at least one head, a head has at
least one eye, and an eye has at least one retina.

\myblock{Attribute Blocks.} Attribute blocks are used to define the
required \emph{datatype} properties of concepts. An attribute block
has the form
\begin{itemize}
\item[]
  \begin{tabular}{|l|l|l|l|l|l|l|}\hline \texttt{attribute} & $P$ & $D$ & $C_1$
    & $C_2$ & \dots & $C_n$ \\ \hline
  \end{tabular} \hfill ($n \ge 1$)
\end{itemize}
where $P$ is a datatype property, each $C_i$ is a concept for $1 \le i
\le n$, and $D$ is a datatype (\texttt{anyValueType}, \texttt{string},
\texttt{int}, etc.). For every concept $C_i$, the property block
induces the DL axiom \[C_i \sqsubseteq (\exists P . D)\] stating that
each instance of $C_i$ has, amongst possibly other things, a
relationship through $P$ to a data value of type $D$.

\myblock{Value Blocks.} Value blocks define required datatype property
\emph{constant values} for concepts. A value block has the form
\begin{itemize}
\item[]
  \begin{tabular}{|l|l|l|l|l|l|l|}\hline \texttt{value} & $P$ & $V$ & $C_1$
    & $C_2$ & \dots & $C_n$ \\ \hline
  \end{tabular} \hfill ($n \ge 1$)
\end{itemize}
where $P$ is a datatype property, $C_i$ is a concept for $1 \le i \le
n$, and $V$ is a datatype value. For each concept $C_i$, the value
block induces the DL axiom \[C_i \sqsubseteq (V \in P)\] stating that
each instance of $C_i$ has a value $V$ for property $P$.  The value
restrictions stated by value blocks are often used for defining
so-called \emph{value partitions} \cite{co-ode}.

\myblock{Inverse Blocks.} Inverse blocks state that two object
properties are inverses of each other. That is, for inverse properties
$P_1$ and $P_2$ and concept instances $O_1$ and $O_2$, if $P_1(O_1) =
O_2$, then $P_2(O_2) = O_1$.  An inverse block has the form
\begin{itemize}
\item[]
  \begin{tabular}{|l|l|l|}\hline \texttt{inverse} & $P_1$ & $P_2$
\\ \hline
  \end{tabular}
\end{itemize}
where $P_1$ and $P_2$ are object properties.

\myblock{Minimum Blocks.} Minimum blocks state the minimum number of
properties $P$ an instance of a concept may have.  Minimum blocks have
the form
\begin{itemize}
\item[]
  \begin{tabular}{|l|l|l|l|l|l|l|}\hline \texttt{minimum} & $P$ & $N$ & 
    $C_1$ & $C_2$ & $\dots$ & $C_m$
    \\ \hline
  \end{tabular}
\end{itemize}
where $N$ is the minimum number of properties $P$ that instances of
concept $C_1$ may have to instances of concept $C_2$, $C_2$ to $C_3$,
and so on. A cardinality block induces the DL axiom \[C_i \sqsubseteq
(\le N P.C_{i+1})\] stating that each instance of $C_i$ must be related to
at least $N$ unique instances of $C_{i+1}$ via $P$. For example, the blocks
\begin{quote}
\texttt{minimum} \texttt{hasPart} 1 \texttt{Body} \texttt{Head} \\
\texttt{minimum} \texttt{hasPart} 2 \texttt{Head} \texttt{Eye}
\end{quote}
states that a body has at least one head and at least two eyes.

\myblock{Maximum Blocks.} Maximum blocks state the maximum
number of properties $P$ an instance of a concept may have.
Maximum blocks have the form
\begin{itemize}
\item[]
  \begin{tabular}{|l|l|l|l|l|l|l|}\hline \texttt{maximum} & $P$ & $N$ & 
    $C_1$ & $C_2$ & $\dots$ & $C_m$
    \\ \hline
  \end{tabular}
\end{itemize}
where $N$ is the maximum number of properties $P$ that instances of
concept $C_1$ may have to instances of concept $C_2$, $C_2$ to $C_3$,
and so on. A cardinality block induces the DL axiom \[C_i \sqsubseteq
(\ge N P.C_{i+1})\] stating that each instance of $C_i$ may be related to
at most $N$ unique instances of $C_{i+1}$ via $P$. For example, the blocks
\begin{quote}
\texttt{maximum} \texttt{hasPart} 1 \texttt{Body} \texttt{Head} \\
\texttt{maximum} \texttt{hasPart} 2 \texttt{Head} \texttt{Eye}
\end{quote}
states that a body has at least one head and at least two eyes.

\myblock{Sufficient Blocks.} Sufficient blocks state that any instance
having a property $P$ to an instance of a concept $C_2$ is a
sufficient condition for being an instance of a concept $C_1$. A
sufficient block has the form
\begin{itemize}
\item[]
  \begin{tabular}{|l|l|l|l|}\hline \texttt{sufficient} & $C_1$ & $P$ & $C_2$
    \\ \hline
  \end{tabular}
\end{itemize}
where $C_1$ is the target concept (i.e., denoting the concept
definition), $P$ is the sufficient property, and $C_2$ is the
sufficient concept. A sufficient block induces the DL axiom \[C_1
\equiv \exists P.C_2\] Sufficient blocks provide a mechansism to
construct simple class definitions (i.e., classes defined precisely by
other classes), primarily for use with value partitions. [NOTE: these
should be anded together?]

\myblock{Description Blocks.} Description blocks assign plain-text
definitions to concepts and properties. A description block has the
form
\begin{itemize}
\item[]
  \begin{tabular}{|l|l|l|}\hline \texttt{description} & $T$ & $S$
    \\ \hline
  \end{tabular}
\end{itemize}
where $T$ is either a property or a concept and $S$ is a description
string.

\myblock{Note Blocks.} Note blocks add comments to the current
ontology, and are ignored by \owlifier.  A note block has the form
\begin{itemize}
\item[]
  \begin{tabular}{|l|l|l|}\hline \texttt{note} & $S$
\\ \hline
  \end{tabular}
\end{itemize}
where $S$ is a comment string.
